---
title: "ExampleRmd"
author: "Cory Thigpen"
date: "January 14, 2018"
output: 
  html_document
  keep_md: true
---
# Introduction
This R markdown document gives the code and output for a function to return the mean of a pollutant across all monitors listed in the 'id' vector (ignoring NA values).

# Specifications
  * 'directory' is a character of length 1 indicating the location of the CSV files (the current working directory)
  * 'pollutant' is a character vector of length 1 indicating the name of the pollutant for which we will calculate the mean; either "sulfate" or "nitrate"
  * 'id' is an integer vector indicating the monitor ID numbers to be used
  
# Important
This data reside in the directory
"C:\Users\william.thigpen\Documents\Data Science\Doing Data Science\Unit 2"

```{r}
setwd("C:/Users/william.thigpen/Documents/Data Science/Doing Data Science/Unit 2")
source("pollutantmean.R")
```
## Change WD to specdata directory
setwd(paste(getwd(),"/specdata",sep=""))
nitrate.mean <- pollutantmean(directory=getwd(),pollutant="nitrate")

```
The mean nitrate content for these stations is 
```{r}
nitrate.mean
```